A double-sampling extension of the German National Forest Inventory for design-based small area estimation on forest district levels

### 2018-05-09 article MDPI/hill et al 2018.tex
update 09_05_2018
update 09_05_2018

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %

@@

% \subsubsection{One- and Two-Phase Sampling in the Infinite Population Approach}

@@

% which in \pkg{forestinventory} is always a linear model fit in $s_2$ using ordinary least squares (OLS).
%The one-phase and two-phase estimators applied in this study have been implemented in the software-package \textit{forestinventory} \cite{forestinventory} 
% The local density $Y(x)$ is in practice derived by ...
% extend the approach to collecting auxiliary information ...
% say that we also assume that the forest area is well-defined ...

@@

% ----------------------------- %
\subsection{Measures of estimation precision}

@@

\begin{equation}\label{eq:releff}
rel.eff=\frac{\hat{\var}_{SRS}(\hat{Y})}{\hat{\var}_{DS}(\hat{Y})}
\end{equation}

\newpage

@@

%This section describes the actual implementation of the proposed small area estimators (Section \ref{sec:estimators}) under the cluster design of the German NFI (Section \ref{sec:germanNFI}) in the federal state Rhineland-Palatinate.

@@

The German federal state Rhineland-Palatinate (\textit{RLP}) is located in the western part of Germany and borders Luxembourg, France and Belgium. With 42.3\% (appr. 8400 km$^2$) of the entire state area (19850 km$^2$) covered by forest, RLP is one of the two states with the highest forest coverage among all federal states of Germany \citep{bwi3}. The forests of RLP are further characterised by a pronounced diversity in bioclimatic growing conditions that have strong influence on the local growth dynamics as well as tree species composition \citep{gauer2005} and are further characterised by large variety of forest structures ranging from characteristic oak coppices (Moselle valley), pure spruce, beech and scots pine forests (i.a. Hunsr{\"u}ck and Palatinate forest) up to mixed forests comprising variable proportions of oak, larch, spruce, Scots pine and beech. Around 82\% of the forest area in RLP are mixed forest stands and 69\% of the forest area exhibit a multi-layered vertical structure. The forest area of RLP are divided into 3 ownership classes, i.e. state forest (27\%), communal forest (46\%) and privately owned forest (27\%). The forest service of RLP has the legal mandate to sustainably manage the state and communal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}. For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (Figure \ref{fig:StudyArea}). On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 405 Forstreviere (\textit{FR}). The next level are the forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5 to 10 year period in order to set up management strategies for the upcoming 10 years. The FAs and FRs constituted the SA units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}. The average area of the SA units was 43'777 ha on the FA-level, and 4624 ha on the FR level.

% | managment level | average area (min-max)  | average no cluster (plots) | min no. cluster (plots | max no. cluster (plots |
%   FA                43'777 ha  (17367 - 125423)     46 (128)                            11 (36)            64 (198)
%   FR                4624 ha   (0.68 - 43284)         5  (14)                            0 (0)             13 (34)
%   stand level       6 ha     (0.03 ha - 73)          0 (0)                              0 (0)             2 (4)

% Add Graphic 1:
% - Graphic of RLP with "zoom" in the 3 managament units (or later all together in Graphic

% Add in text:
% - add information on the (average) spatial area of each sae-level

% Notes to myself:
% - in the original forstrevier layer, we have 427 FR units but 21 of them are not covered by woefis-layer (so no state- and communal forest), and 1 is the "Bundesforstamt" not considered by us

@@

\begin{figure}[H]
	\centering
	\resizebox{0.85\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
	\caption{\textit{Left}: Study area with delineated FA forest management units. \textit{Right}: Example for each of the three management units (from top to bottom): FA, FR and forest stand unit overlayed with the extended double-sampling cluster design. \textit{Green}: Forest stand polygon layer defining the forest area of this study.}
	\label{fig:StudyArea}
\end{figure}

@@

In order to apply the small area estimators (Section \ref{sec:SAestimators}), the existing NFI design was extended to a double-sampling design by densifying the existing systematic 2x2 km grid to a grid size of 500x500 m that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArea}, \textit{right}). The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ clusters by the terrestrially measured DGPS coordinates. For our study, we restricted the sampling frame to the communal and state forest. The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stands provided by the forest service. Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame. The terrestrial sample size $n_2$ was thus reduced to 2055 clusters (5791 plots). Table \ref{tab:fieldata} provides a short descriptive summary about the volume densities and the main attributes of the NFI plots located in the state and communal forest sampling frame. The densification led to an average sample size $n_{1,G}$ of 759  clusters (range: 246 -- 1022) in the FA units, and 88 clusters (range: 1 -- 194) in the FR units.

@@

% NOTES:
%
% Add Table:
% provide table of "forest characteristics" in RLP
% adress sample sizes before and after extension (table?)
%
% move this to discussion:
% It should however be mentioned that a discrepancy between the terrestrially made forest/non-forest decision and that based on the polygon stand layer can lead to missing responses in the terrestrial sample $s_2$. This occurs if a terrestrial plot $x_l \in s_2$ does not provide the terrestrial response variable although its plot center would theoretically fall within the boundaries of the stand layer. For these cases, it is important to note that according to the double sampling estimator described in Section \ref{sec:SAestimators}, the plots of a cluster can either only belong to the sample $s_2$ or $s_1$. The missing terrestrial plot information $Y(x)$ can thus not be replaced by a prediction $\hat{Y}(x)$, i.e. by establishing a plot $x \in s_1$ instead, and has thus to be treated as a non-response.\par
%
%  "This extension led to a considerable increase of the sample size $n_{1,G}$ in the small area units of both, the FA and FR level."
% - Show (theoretical) increase in sample sizes by extension to 2phase scheme 
%   --> these sample sizes are in the following reduced by missing rs-info
%

% ----------------------------------------------------------------------- %
% Table xx provides an overview of the terrestrial sample sizes on these management levels for the state and communal forest areas.

% \input{terrSamplsizeFoaFuWa.tex}

% average no. plots / clusters; average area of all three units (divided by state + communal forest & entire forest area)

% --> this is only for communal & state forest area:
% | managment level | average area (min-max)  | average no cluster (plots) | min no. cluster (plots | max no. cluster (plots |
%   FA                43'777 ha  (17367 - 125423)     46 (128)         11 (36)            64 (198)
%   FR                4624 ha   (0.68 - 43284)         5  (14)          0 (0)             13 (34)
%   stand level       6 ha     (0.03 ha - 73)          0 (0)            0 (0)             2 (4)

% - Verwaltungsebenen: management levels (Forstamt, Revier, Bestände) -> durschnittliche Flächengrössen (für die sollen die sae schätzungen gemacht werden)
% - evtl bereits Stichprobenzahlen generell und innerhalb der Managementenheiten nennen (das ginge dirket hinsichltich des eigentlichen Themas)
%   (das generelle Problem der Stichprobenanzahl in diesen Einheiten wurde ja schon in der Einleitung angesprochen, also könnte man
%    hier direkt ein Beispiel geben) --> hier noch getrennt nach gesamter Wald und nur Woefis-Wald (Tabelle, Grpahik)
% - warum RLP ? (neues Informationssystem, Interesse an effizienteren Methoden)
% wir nennen Fortamt einfach 'FA-level' und Forstrevier einfach 'FR-level' :-)
% Info: 45 Forstämter without Bundesforstamt; 426 Reviere without Bundesforstamt
% mention that the boundaries of all these management units are well-defined by polygon masks (that were used to extract the sampling
% frame)
% ----------------------------------------------------------------------- %

@@

%% Here is the table with calibrated and uncalibrated values:
%\begin{table}[H]
%	\begin{center}
%	\caption{Classification accuracies of the \textit{treespecies} variable before and after calibration. $n_{ref}$: number of terrestrial reference plots. $n_{class}$: number of classified plots.}
%	\vspace{0.2cm}
%	\label{tab:classacc}
% {\small %
%	\begin{tabular}{l|c c|c c|c|c c} %8cols
%		\hlineB{1}
%		\multirow{2}{*}{Main plot species} & \multicolumn{2}{c|}{Producer's accuracy[\%]} & \multicolumn{2}{c|}{User's accuracy[\%]} & \multirow{2}{*}{nref} & \multicolumn{2}{c}{nclass} \\ 
%		\cline{2-3} \cline{4-5} \cline{7-8} & uncalib & calib & uncalib & calib & & uncalib & calib \\
%		\hline \hline	
%		 Beech       & 29.56 & 22.31 & 46.11 & 47.02 & 883 & 566 & 419 \\
%		 Douglas Fir & 33.04 & 24.78 & 47.50 & 48.72 & 230 & 160 & 117 \\
%		 Oak         & 47.75 & 11.07 & 24.34 & 48.48 & 289 & 567 & 66 \\
%		 Spruce      & 43.63 & 53.15 & 60.81 & 61.13 & 651 & 467 & 566 \\
%		 Scots Pine  & 55.87 & 22.91 & 29.59 & 46.07 & 179 & 338 & 89 \\
%		 Mixed       & 66.40 & 84.49 & 63.69 & 64.53 & 3152 & 3286 & 4127 \\
%		\hline
%		 & \multicolumn{4}{l|}{Overall accuracy: 54.83\% (61.96\%)} & 5384 & \multicolumn{2}{c}{5384} \\
%		 \hline \hline
%	\end{tabular}
%}%
%	\end{center}
%\end{table}

@@

The model selection process for this study required a substantial time commitment due to sophisticated challenges such as: a) the heterogeneity of the remote sensing data, b) the identification of the optimal support sizes under angle count sampling, and c) the incorporation of tree species information. Here, only a summary of the extensive analysis that was performed is provided but the reader can refer to \citet{hill2017a} if more details are desired\par
The model with highest \adjrsq{} and lowest RMSE was achieved using \meanheight{}, \meanheight{}$^2$, \stddev{}, \alsyear{} and \treespecies{} as main effects, and including interaction terms between \meanheight{} and \alsyear{}, \stddev{} and \alsyear{}, \meanheight{} and \stddev{}, and \meanheight{} and \treespecies{}. Summary information about the \adjrsq{}, RMSE and RMSE\% of the selected models is provided in Table \ref{tab:modacc_modterms}. The two-phase estimators described in Section \ref{sec:SAestimators} derive and apply the regression coefficients and the residuals on the aggregated cluster level. We re-evaluated the model as used in the estimators on the cluster level (formulas given in Appendix) and found improved model fits compared to the plot level (\adjrsq{} of 0.59 and RMSE of 101.61 \mha{} and 33.6\%). The stratification by the ALS acquisition year substantially improved the model fit, indicating that it is an effective means in accounting for the noise in the data caused by ALS quality variations and time-gaps between the ALS and the terrestrial survey. However, the stratification led to a highly unbalanced data set when a further \treespecies{} stratification was included. For this reason, a individual species modeling within each \alsyear{} stratum remained infeasible, but might have further improved the model fit. An additional evaluation of the model's performance within each ALS acquisition year stratum revealed that the quality of the model fit substantially varied between the strata (Table \ref{tab:adj_r2_within}). In particular, values above the overall \adjrsq{} were higher in ALS acquisition years close to the terrestrial survey date compared to years with larger time gaps.\par
As described in Section \ref{sec:tspecclass}, the information of the tree species classification map was missing within 1 FA and 19 FR units. For these small area units, we applied the regression model without the \treespecies{} variable (Table \ref{tab:modacc_modterms}, reduced model). However, the \adjrsq{}s of the full and reduced model were found to be very similar on both the plot and cluster level. This implied that the variance reduction of the reduced model when applied to the two-phase estimators would likely be comparable to that of the full model, which is why a joint evaluation of the estimation results was performed (Section \ref{sec:Res}).

>>>>

%  LaTeX support: latex@mdpi.com 
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.

%=================================================================
\documentclass[remotesensing,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi} 
%
%--------------------
% Class Options:
%--------------------
% journal
%----------
% Choose between the following MDPI journals:
% actuators, addictions, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, ceramics, challenges, chemengineering, chemosensors, children, chromatography, climate, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cybersecurity, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electrochemistry, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forests, fractalfract, futureinternet, galaxies, games, gastrointestdisord, gels, genealogy, genes, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, ijtpp, inventions, j, jcdd, jcm, jcs, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmmp, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nitrogen, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, plasma, polymers, preprints, proceedings, processes, proteomes, publications, quaternary, qubs, recycling, religions, remotesensing, resources, risks, robotics, safety, scipharm, sensors, separations, sexes, sinusitis, socsci, societies, soils, sports, standards, surgeries, sustainability, symmetry, systems, technologies, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vetsci, vibration, viruses, vision, water, wem
%---------
% article
%---------
% The default type of manuscript is article, but can be replaced by: 
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferenceproceedings, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, opinion, obituary, projectreport, reply, reprint, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials
% protocol: If you are preparing a "Protocol" paper, please refer to http://www.mdpi.com/journal/mps/instructions for details on its expected structure and content.
%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g. the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother 
\articlenumber{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2017}
\copyrightyear{2017}
\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}

\usepackage{gensymb}
\usepackage{natbib}
\usepackage{tabulary}
\usepackage{multirow}
\usepackage{boldline}

\usepackage[british]{babel}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{graphicx}

\usepackage[font=footnotesize]{caption}
\usepackage[font=footnotesize]{subcaption}

\definecolor{mygreen}{rgb}{0.1, 0.6, 0.4}
\newcommand{\added}[1]{\color{mygreen}{#1} \color{black}}
\newcommand{\changed}[1]{\color{red}{#1} \color{black}}

\newcommand{\adjrsq}{adjusted $R^2$}
\newcommand{\rmsecv}{RMSE$_{cv}$}
\newcommand{\mha}{m$^3$/ha}
\newcommand{\bwi}{BWI3}
\newcommand{\psynth}{PSYNTH}
\newcommand{\psmall}{PSMALL}
\newcommand{\extpsynth}{EXTPSYNTH}
\newcommand{\meanheight}{\textit{meanheight}}
\newcommand{\stddev}{\textit{stddev}}
\newcommand{\treespecies}{\textit{treespecies}}
\newcommand{\alsyear}{\textit{ALSyear}}
\newcommand{\var}{\mathbb{V}}
\newcommand{\EX}{\mathbb{E}}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{A double-sampling extension of the German National Forest Inventory for design-based small area estimation on forest district levels}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-6367-2256} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Andreas Hill $^{1,}$*\orcidA{}, Daniel Mandallaz $^{1}$ and Joachim Langshausen $^{2}$}

% Authors, for metadata in PDF
\AuthorNames{Andreas Hill, Daniel Mandallaz and Joachim Langshausen}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
	$^{1}$ \quad Department of Environmental Systems Science, ETH Zurich, 8092 Zurich, Switzerland; mdaniel@retired.ethz.ch (D.M.)\\
	$^{2}$ \quad State Forest Service Rhineland-Palatinate, 56281 Emmelshausen, Germany; Joachim.Langshausen@wald-rlp.de}

% Contact information of the corresponding author
\corres{Correspondence: andreas.hill@usys.ethz.ch; Tel.: +x-xxx-xxx-xxxx}

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{The German National Forest Inventory consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests on national and federal state level in a 10 year interval. However, the data have yet been scarcely used for estimation on smaller management levels such as forest districts due to insufficient sample sizes within the area of interests and the implied large estimation errors. In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area regression estimators. We illustrate the implementation of the estimation procedure and evaluate its potential by the example of timber volume estimation on two small scale management levels (45 and 405 forest district units respectively) in the federal German state of Rhineland-Palatinate. An airborne laserscanning (ALS) derived canopy height model and a tree species classification map based on satellite data were used as auxiliary data in an ordinary least square regression model to produce the timber volume predictions. The results support that the suggested double-sampling procedure can substantially increase estimation precision on both management levels: the two-phase estimators were able to reduce the variance of the SRS estimator by 43\% and 25\% on average for the two management levels respectively.}

% Keywords
\keyword{National forest inventory, small area estimation, forest districts, double sampling for regression within strata, cluster sampling, canopy height model, tree species classification}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for the journal Gels: Please place the Experimental Section after the Conclusions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{section}{-1} %% Remove this when starting to work on the template.
%\section{How to Use this Template}
%The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g. the positioning of the Materials and Methods section). Please check the instructions for authors page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.

\section{Introduction}
\label{sec:intro}

The German National Forest Inventory (NFI) provides reliable evidence-based and accurate information of the current state and the development of Germany's forest over time. The NFI thereby has the responsibility to satisfy various information needs including reporting to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and to the United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}. The current design of the German NFI rests solely upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forest state area of Germany. In order to cover a large area of 114'191 ha \citep{bwi3}, the sample size has been specifically chosen to satisfy high estimation accuracies for forest attributes on the national and federal state levels. However, sample sizes often drop dramatically when entering spatial units below the federal state level. This is particularly true for forest management levels such as forest districts for which the estimation uncertainties turn out to be unacceptably large due to the very limited number of sample plots within these units. For this reason, the German NFI data have not yet been extensively incorporated into operational planning on forest district management levels. In most German federal states, management strategies are thus still based on expert judgments from time-consuming standwise inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par

Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) with a much higher sampling density than used by the NFI in order to scientifically base their regional management strategies on quantitative and accurate information \citep{bockmann1998}. However, such FDIs are cost-intensive and, facing increasing restrictions in budget and staff resources, there has been a need for more cost-efficient inventory methods \citep{vonluepke2013}. One method which has proven to be efficient is double- or two-phase sampling \citep{sarndal2003, gregoire2007, kohl2006, mandallaz2008}. Double-sampling incorporates less expensive auxiliary information and can be used to either increase estimation precision under a fixed terrestrial sample size, or maintain estimation precision under reduced terrestrial sample size. Double-sampling procedures have already been used for stratification in the FDI of Lower Saxony \citep{saborowski2010}, and \citet{grafstrom2017a} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs. Recent studies have extended double-sampling to triple-sampling estimation methods using auxiliary information derived at two different sampling intensities. An example can be found in \citet{vonLuepke2012} who illustrated an extension of the existing two-phase FDI of Lower Saxony to a three-phase design that uses updates of past inventory data as additional auxiliary information and allows for a significant reduction of the terrestrial sample size in intermediate inventories. Another example is \citet{massey2014a} who developed a triple-sampling extension based on the ideas of \citet{mandallaz2013c} for the Swiss NFI that can significantly reduce the increase in estimation uncertainty caused by the new annual inventory design.\par

Two-phase and three-phase samplings techniques have also been applied to small area estimation (SAE). SAE techniques address the situation where the number of samples within a subunit, or small area (SA), of the entire sampling frame is too small to provide reliable estimates for that unit. A broad range of SA estimators used in forest inventories \citep{kohl2006} originally comes from official statistics. One such method that is commonly applied is known as indirect estimation \citep{rao2015}, where statistical models are used to convert auxiliary information into predictions of the target variable that is rarely or not observed in the small area. These models are trained using data from outside the small area in order to "borrow strength" from areas where information is available. Of numerous applications of SAE in forestry \citep{breidenbach2012, goerndt2011, steinmann2013, mandallaz2013b}, most use unit-level models, i.e. the inventory plot is the unit of the response variable in the training data used for the model fit. Such unit-level models have been intensively investigated for timber volume estimation using various remote sensing auxiliary data \citep{koch2010, naesset2014inmaltamo}. Other studies have investigated area-level models, where the auxiliary information is only provided on the SA level \citep{magnussen2017}. Some studies have illustrated that even NFI data derived under low sampling densities can still be used to provide acceptable precision of small area estimates on much smaller management levels. One example is \citet{breidenbach2012} who used data from the Norwegian NFI to make small area estimation for standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35. The estimation errors under the applied model-dependent and design-based small area estimators turned to be markedly smaller than under the standard one-phase estimator. Another example is \citet{magnussen2014} who recently used the Swiss NFI data to estimate timber volume within 108 Swiss forest districts with sample sizes between 9 and 206. Similar studies using German NFI data for small area estimation have been lacking.\par

The aim of this study was to investigate whether the German NFI data can provide acceptable estimation precision on two forest district levels using the latest small area estimation procedures. We therefore conducted a study in the German federal state Rhineland-Palatinate where we extended the German NFI to a double-sampling design and applied three types of design-based small area regression estimators in order to derive point and variance estimates of mean standing timber volume for 45 and 405 forest districts respectively. The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a} and \citet{ mandallaz2013b}. Auxiliary data consisted of a canopy height model (CHM) obtained from a countrywide airborne laser scanning (ALS) and a tree species classification map to be used for regression within tree species strata. The estimation precisions were compared to those obtained by the standard one-phase estimator for cluster sampling under simple random sampling. The chosen double-sampling estimators were selected for several reasons: \textbf{(i)} the design-based framework relaxes dependencies on the regression model assumptions which seemed appropriate facing severe quality restrictions in the ALS data; \textbf{(ii)} the estimators can be used with \textit{non-exhaustive}, i.e. non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for estimating the regression coefficients on the same sample used for estimation (\textit{internal model approach}) and is also robust under heteroscedasticity of the model residuals. The results from this study were considered to provide valuable information whether the suggested procedure might be a cost-saving alternative to a regional FDI.\par

%---------------------------------------------------------------------------------------------------------%
% ---------------------------------- Materials and Methods ---------------------------------------------- %

@@

 \subsubsection{One- and Two-Phase Sampling in the Infinite Population Approach}

@@

@@

% ----------------------------- %
\subsection{Measures of estimation accuracy}

@@

\begin{equation}\label{eq:releff}
rel.eff=\frac{\hat{\var}(\hat{Y}_{SRS})}{\hat{\var}(\hat{Y}_{DS})}
\end{equation}

@@

@@

The German federal state Rhineland-Palatinate (\textit{RLP}) is located in the western part of Germany and borders Luxembourg, France and Belgium. With 42.3\% (appr. 8400 km$^2$) of the entire state area (19850 km$^2$) covered by forest, RLP is one of the two states with the highest forest coverage among all federal states of Germany \citep{bwi3}. The forests of RLP are further characterised by a pronounced diversity in bioclimatic growing conditions that have strong influence on the local growth dynamics as well as tree species composition \citep{gauer2005} and are further characterised by large variety of forest structures ranging from characteristic oak coppices (Moselle valley), pure spruce, beech and scots pine forests (i.a. Hunsr{\"u}ck and Palatinate forest) up to mixed forests comprising variable proportions of oak, larch, spruce, Scots pine and beech. Around 82\% of the forest area in RLP are mixed forest stands and 69\% of the forest area exhibit a multi-layered vertical structure. The forest area of RLP are divided into 3 ownership classes, i.e. state forest (27\%), communal forest (46\%) and privately owned forest (27\%). The forest service of RLP has the legal mandate to sustainably manage the state and communal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}. For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (Figure \ref{fig:StudyArean}). On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 405 Forstreviere (\textit{FR}). The next level are the forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5 to 10 year period in order to set up management strategies for the upcoming 10 years. The FAs and FRs constituted the SA units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}. The average area of the SA units was 43'777 ha on the FA-level, and 4624 ha on the FR level.

@@

\begin{figure}[H]
	\centering
	\resizebox{0.85\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
	\caption{\textit{Left}: Study area with delineated FA forest management units. \textit{Right}: Example for each of the three management units (from top to bottom): FA, FR and forest stand unit overlayed with the extended double-sampling cluster design. \textit{Green}: Forest stand polygon layer defining the forest area of this study.}
	\label{fig:StudyArean}
\end{figure}

@@

In order to apply the small area estimators (Section \ref{sec:SAestimators}), the existing NFI design was extended to a double-sampling design by densifying the existing systematic 2x2 km grid to a grid size of 500x500 m that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure \ref{fig:StudyArean}, \textit{right}). The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ clusters by the terrestrially measured DGPS coordinates. For our study, we restricted the sampling frame to the communal and state forest. The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stands provided by the forest service. Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame. The terrestrial sample size $n_2$ was thus reduced to 2055 clusters (5791 plots). Table \ref{tab:fieldata} provides a short descriptive summary about the volume densities and the main attributes of the NFI plots located in the state and communal forest sampling frame. The densification led to an average sample size $n_{1,G}$ of 759  clusters (range: 246 -- 1022) in the FA units, and 88 clusters (range: 1 -- 194) in the FR units.

@@

@@

@@

The model selection process for this study required a substantial time commitment due to sophisticated challenges such as: a) the heterogeneity of the remote sensing data, b) the identification of the optimal support sizes under angle count sampling, and c) the incorporation of tree species information. Here, only a summary of the extensive analysis that was performed is provided but the reader can refer to \citet{hill2017a} if more details are desired.\par
The model with highest \adjrsq{} and lowest RMSE was achieved using \meanheight{}, \meanheight{}$^2$, \stddev{}, \alsyear{} and \treespecies{} as main effects, and including interaction terms between \meanheight{} and \alsyear{}, \stddev{} and \alsyear{}, \meanheight{} and \stddev{}, and \meanheight{} and \treespecies{}. Summary information about the \adjrsq{}, RMSE and RMSE\% of the selected models is provided in Table \ref{tab:modacc_modterms}. As the two-phase estimators described in Section \ref{sec:SAestimators} derive and apply the regression coefficients and the residuals on the aggregated cluster level, we re-evaluated the model as used in the estimators on the cluster level (formulas given in Appendix) and found improved model fits compared to the plot level (\adjrsq{} of 0.59 and RMSE of 101.61 \mha{} and 33.6\%). The stratification by the ALS acquisition year substantially improved the model fit, indicating that it is an effective means in accounting for the noise in the data caused by ALS quality variations and time-gaps between the ALS and the terrestrial survey. However, the stratification led to a highly unbalanced data set when a further \treespecies{} stratification was included. For this reason, a individual species modeling within each \alsyear{} stratum remained infeasible, but might have further improved the model fit. An additional evaluation of the model's performance within each ALS acquisition year stratum revealed that the quality of the model fit substantially varied between the strata (Table \ref{tab:adj_r2_within}). In particular, values above the overall \adjrsq{} were higher in ALS acquisition years close to the terrestrial survey date compared to years with larger time gaps.\par
As described in Section \ref{sec:tspecclass}, the information of the tree species classification map was missing within 1 FA and 19 FR units. For these small area units, we applied the regression model without the \treespecies{} variable (Table \ref{tab:modacc_modterms}, reduced model). However, the \adjrsq{}s of the full and reduced model were found to be very similar on both the plot and cluster level. This implied that the variance reduction of the reduced model when applied to the two-phase estimators would likely be comparable to that of the full model, which is why a joint evaluation of the estimation results was performed (Section \ref{sec:Res}).
